Making Sequential Programs Deterministic

### 2019-04-05 related.tex
more related

>>>>

Failing tests that are unrelated to code changes can be expensive both in terms of monetary costs and
developer effort. \cite{Herzig:2015:EDF:2819009.2819018} propose techniques to classify tests as false alarms
if they are known to be caused by testing infrastructure or other environment issues.~\cite{Huo:2014:IOQ:2635868.2635917}
propose an approach that detects brittle assertions in tests by performing a taint analysis on inputs classified as 
controlled and uncontrolled.~\cite{ZhangJWMLEN2014} investigate the effects of test independence assumption
on other techniques such as test prioritization, selection, etc. 
\cite{BellKMD2015}
\cite{Gyori:2015:RTD:2771783.2771793}
\cite{Dan:2013:10.1007/978-3-642-39038-8_25}
\cite{Vahabzadeh:2015:7332456}
\cite{Fowler}
\cite{Sudarshan}
